Results

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added participant info

---
title: "results"
author: "Christoph Scheffel"
output: html_document
---

@@

#library(papaja)     # APA conform output
#library(readxl)     # import excel files
```

@@

Data collection took place between `r acqui_time[1]` and `r acqui_time[2]`.

>>>>

---
title: "Results"
author: "Christoph Scheffel"
output: html_document
---

@@

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
```

@@

Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`. A total of $N=`r sum(data_survey$lay_beliefs_complete == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions. Of these, $N=`r sum(data_survey$files_coged_complete == 2)`$ participated in the first laboratory session and $N=`r sum(data_survey$followup_ered_complete == 2)`$ completed the second laboratory session. Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
